Triplots and Output Elasticities

### 2015-09-16 Testing/Elasticity.Rmd
work around for ggplot2 "bug" using data_frame()
update labeling

  ggplot() +
    tri_theme() +
    tri_grid() +
    tri_labels(labels = c("k", "l", "e"), parse = TRUE) +
    geom_tripath( 
      data = data, aes(x=oe1, y=oe2, z=oe3),
      alpha=0.6, colour = "black") +
    geom_tripoint( 
      data = data, aes(x=oe1, y=oe2, z=oe3, colour = Year), 
      alpha=0.6) +
    scale_colour_gradient(low = scales::muted("navy"),  high = "green") +
    facet_grid( ~ Country)
}
```

@@

## Side note about bug in ggplot2

```{r}
  ggplot() +
    geom_text(
      data = data.frame(x = 0, y = 0, label = "alpha[1]"),
      parse = TRUE,
      aes(x=x, y=y, label=label)
    )

  ggplot() +
    geom_text(
      data = data.frame(x = 0, y = 0),
      parse = TRUE,
      aes(x=x, y=y, label=label),
      label = "alpha[1]"
    ) 
```

>>>>

  ggplot() +
    tri_theme() +
    tri_grid() +
    tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]"), parse = TRUE) +
    geom_tripath( 
      data = data, aes(x=oe1, y=oe2, z=oe3),
      alpha=0.6, colour = "black") +
    geom_tripoint( 
      data = data, aes(x=oe1, y=oe2, z=oe3, colour = Year), 
      alpha=0.6) +
    scale_colour_gradient(low = scales::muted("navy"),  high = "green") +
    facet_grid( ~ Country)
}
```

@@
